---
title: 'Part 1: Binary Logistic Regression'
author: "Kirsten Hodgson"
date: "1/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create a subset with only Adelie and Chinstrap penguins:
```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species)) #drop any factor levels with 0 observations (gentoo) here for binom
```

Let's just dataviz of those two species:
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex)) +
  facet_wrap(~species)
```

Binary logistic regression

- body mass
- flipper length
- penguin sex

```{r}
adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm + sex,
                            data = adelie_chinstrap,
                            family = "binomial")
```

Take a look at the outcomes:
```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)
```

Coefficient of body mass: -8.6e-4
- This means that the probability of Chinstrap penguin (which is the non-zero level, found by running levels(chinstrap_adelie$species) in console) decreases with increase in body mass

Positive coefficient of flipper length means that increases in flipper length increases probability of Chinstrap penguin

Interpretation of the sex coefficient is a little funky this time.

```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = flipper_length_mm)) +
  geom_jitter(aes(color = sex))
```

What are the actual probabilities of being Chinstrap for each of the existing observations in our adelie_chinstrap dataframe?

```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")
```

Plotting the fitted probabilities of being a Chinstrap penguin:
```{r}
ggplot(data = blr_fitted, aes(x = flipper_length_mm, y = .fitted)) +
  geom_point(aes(color = sex, pch = species)) +
  geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper Length (mm",
       y = "Probability of Outcome Chinstrap")
```

Plot model based on different variables:
```{r}
#From jtools, not great for customaization but useful for quick overviews of the probability relationship
effect_plot(adelie_chinstrap_blr,
            pred = flipper_length_mm,
            y.label = "Probability of Chinstrap",
            interval = TRUE)

effect_plot(adelie_chinstrap_blr,
            pred = body_mass_g,
            y.label = "Probability of Chinstrap",
            interval = TRUE)
```

What's the probability that a female penguin weighing 3410 g with a flipper length of 192 mm is a Chinstrap?

```{r}
ex_1 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female",
                           body_mass_g = 3410,
                           flipper_length_mm = 192),
                type = "response") #this line converts from log odds to probability

ex_1
```

